Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-29 manuscript.Rmd

exp.05 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.05[i] <- exp.05[i-1] + exp.05[i-1]*.05
}

exp.04 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.04[i] <- exp.04[i-1] + exp.04[i-1]*.04
}

exp.03 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.03[i] <- exp.03[i-1] + exp.03[i-1]*.03
}

n.journals.year$exp.05 <- exp.05
n.journals.year$exp.04 <- exp.04
n.journals.year$exp.03 <- exp.03
n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
n.journals.year <- as.data.frame(n.journals.year)

@@

cols = c("Observed Growth" = cp[1], "Estimated 3.2% CAGR" = cp[4], "Estimated 5% CAGR" = cp[3])

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))
```

@@

figure3 <- ggplot(annualChange.df, aes(year, annualChange.numeric, fill =annualChange.dichotomous)) + 
    theme_bw() + 
    geom_bar(stat="identity") +
    scale_fill_manual(values = cp[c(3,1)], limits = c("Increase", "Decrease")) + 
    theme(legend.position = c(1,1), legend.justification = c(1,1), legend.title = element_blank()) + 
    ylab("Percent change") +
    xlab("Year")  +
    scale_x_continuous(breaks=seq(1989, 2015, 4)) + 
    scale_y_continuous(breaks = seq(-10, 15, 5)) + 
    geom_hline(yintercept=seq(-5, 15, 5), col="white", lwd=0.4) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) + 
    geom_hline(yintercept=0, col="gray", lwd=0.6, alpha =.8) +
    ggtitle("Figure 3. Annual Percentage Change in the Number Journals (1989 - 2013)") +
    theme(plot.title = element_text(size = 19))

>>>>

exp.047 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.047[i] <- exp.047[i-1] + exp.047[i-1]*.047
}

exp.0321 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.0321[i] <- exp.0321[i-1] + exp.0321[i-1]*.0321
}

n.journals.year$Price <- exp.047
n.journals.year$SWHD <- exp.0321
n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
n.journals.year <- as.data.frame(n.journals.year)

@@

cols = c("Observed Growth" = cp[1], "3.21% CAGR" = cp[4], "4.7% CAGR" = cp[3])

(figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19)))
```

@@

figure3 <- ggplot(annualChange.df, aes(year, annualChange.numeric, fill =annualChange.dichotomous)) + 
    theme_bw() + 
    geom_bar(stat="identity") +
    scale_fill_manual(values = cp[c(3,1)], limits = c("Increase", "Decrease")) + 
    theme(legend.position = c(1,1), legend.justification = c(1,1), legend.title = element_blank()) + 
    ylab("Percent change") +
    xlab("Year")  +
    scale_x_continuous(breaks=seq(1989, 2015, 4)) + 
    scale_y_continuous(breaks = seq(-10, 15, 5)) + 
    geom_hline(yintercept=seq(-5, 15, 5), col="white", lwd=0.4) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) + 
    geom_hline(yintercept=0, col="gray", lwd=0.6, alpha =.8) +
    #ggtitle("Figure 3. Annual Percentage Change in the Number Journals (1989 - 2013)") +
    theme(plot.title = element_text(size = 19))
